Something something

### 2024-08-28 paper/ms.tex
Add alpha tform text

@@

>>>>

\subsection{Alpha Time Dependence}\label{ssec:alpha_time}

@@

The abundance distributions shown in Figure~\ref{fig:fig1} can be better understood by examining the evolution of \MgFe{} with time of the individual stars/star particles. In the upper panels of Figure~\ref{fig:alpha} we show the true distribution of \MgFe{} as a function of time for the fiducial SOI in the middle and for the post-processed, $\alpha$-enhanced subhalo to the right. We split  We use age instead of formation time in order to better facilitate comparisons to observations. There is a gap in the ages that occurs at an age of  $\sim10.75\,\Gyr$, which we mark with a vertical dashed line. Star particles older than this line have a much clearer gradient in time with \MgFe{} than stars that form after. In the $\FeH=-0.25$ bin, star particles which form directly after this line have a slightly depressed \MgFe{} than stars which form a short time later.

In the lower panels we plot to the left data from the Milky Way and to the middle and right from the fiducial and $\alpha$-enhanced SOI, respectively. For the simulations, we add $10\%$ age and $0.01\,\dex$ \MgFe{} errors. These values are roughly in line with the observational errors from the APOKASC2 and APOGEE datasets that the lower left panel is made from (see Appendix~\ref{app:errors} for plots of the observational errors). The error in \MgFe{} is not signficant, but the age error of $1\,\Gyr$ at $10\,\Gyr$ smears out the distribution before and after the dashed line. The $\alpha$-enhanced SOI still shows two separate populations in this plot, but they now significantly overlap in age.

The Milky Way distribution (lower left panel) bears some resemblance to the $\alpha$-enhanced SOI. In particular, the $\FeH=-0.5$ and $-0.25$ bins (blue and orange, respectively) show what appears to be two populations overlapping in age but nonetheless separated in \MgFe{}.
